### 2023-02-04 glossaries/acronyms.tex
Add gls style for symbols and other fixes
up

\newacronym[symbol={\mathrm{CHL}}]
    {chl}{Chl-\emph{a}}{Chlorophyll-\emph{a}}
\newacronym[symbol={\mathrm{SST}}]
    {SST}{SST}{Sea Surface Temperature}

\newacronym[symbol={\mathrm{HI}}]
    {HI}{HI}{Heterogeneity Index}

\newacronym{AVHRR}{AVHRR}{Advanced Very-High-Resolution Radiometer}
\newacronym{VIIRS}{VIIRS}{Visible Infrared Imaging Radiometer Suite}
\newacronym{MODIS}{MODIS}{Moderate Resolution Imaging Spectroradiometer}
\newacronym[sort=AATSR]{ATSR}{(A)ATSR}{(Advanced) Along Track-Scanning Radiometer}
\newacronym{SeaWiFS}{SeaWiFS}{Sea-viewing Wild Field-of-view Sensor}
\newacronym{MERIS}{MERIS}{Medium Resolution Imaging Spectrometer}
\newacronym{OLCI}{OLCI}{Ocean and Land Colour Instrument}

\newacronym{NOAA}{NOAA}{National Oceanic and Atmospheric Administration}
\newacronym{ERS}{ERS}{European Remote Sensing}
\newacronym{MetOp}{MetOp}{Meteorological Operational satellite}
\newacronym{SNPP}{Suomi~NPP}{Suomi National Polar-orbiting Partnership}

\newacronym{GHRSST}{GHRSST}{Group for High Resolution Sea Surface Temperature}
\newacronym{MUR}{MUR}{Multiscale Ultrahigh Resolution}

\newacronym{ESA}{ESA}{European Space Agency}
\newacronym{CCI}{CCI}{Climate Change Initiative}
\newacronym{C3S}{C3S}{Copernicus Climate Change Service}
\newacronym{OSTIA}{OSTIA}{Operational Sea Surface Temperature and Sea Ice Analysis}
\newacronym{OCSSW}{OCSSW}{OceanColor Science Software}

\newacronym{CMEMS}{CMEMS}{Copernicus Marine Environment Monitoring Service}
\newacronym{CF}{CF}{Climate Forecast (convention for NetCDF)}

\newacronym
[description={Groupe fonctionnel phytoplanctonique}]
{PFT}{PFT}{Phytoplanktonic Function Type}

>>>>

\newacronym[symbol={\mathrm{CHL}}, sort=ChlA]
    {chl}{Chl\babelhyphen{nobreak}\emph{a}}{Chlorophyll\babelhyphen{nobreak}\emph{a}}
\newacronym[symbol={\mathrm{SST}}]
    {sst}{SST}{Sea Surface Temperature}

\newacronym[symbol={\mathrm{HI}}]
    {hi}{HI}{Heterogeneity Index}

\newacronym{avhrr}{AVHRR}{Advanced Very"-High"-Resolution Radiometer}
\newacronym{viirs}{VIIRS}{Visible Infrared Imaging Radiometer Suite}
\newacronym{modis}{MODIS}{Moderate Resolution Imaging Spectroradiometer}
\newacronym[sort=AATSR]{atsr}{(A)ATSR}{(Advanced) Along Track"-Scanning Radiometer}
\newacronym{seawifs}{SeaWiFS}{Sea-viewing Wild Field"-of"-view Sensor}
\newacronym{meris}{MERIS}{Medium Resolution Imaging Spectrometer}
\newacronym{olci}{OLCI}{Ocean and Land Colour Instrument}

\newacronym{noaa}{NOAA}{National Oceanic and Atmospheric Administration}
\newacronym{ers}{ERS}{European Remote Sensing}
\newacronym{metop}{MetOp}{Meteorological Operational satellite}
\newacronym{snpp}{Suomi~NPP}{Suomi National Polar"-orbiting Partnership}

\newacronym{ghrsst}{GHRSST}{Group for High Resolution Sea Surface Temperature}
\newacronym{mur}{MUR}{Multiscale Ultrahigh Resolution}

\newacronym{esa}{ESA}{European Space Agency}
\newacronym{cci}{CCI}{Climate Change Initiative}
\newacronym{c3s}{C3S}{Copernicus Climate Change Service}
\newacronym{ostia}{OSTIA}{Operational Sea Surface Temperature and Sea Ice Analysis}
\newacronym{ocssw}{OCSSW}{OceanColor Science Software}

\newacronym{cmems}{CMEMS}{Copernicus Marine Environment Monitoring Service}
\newacronym{cf}{CF}{Climate Forecast (convention for NetCDF)}

\newacronym
[description={Groupe fonctionnel phytoplanctonique}]
{pft}{PFT}{Phytoplanktonic Function Type}
